Mathematical appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-22 src/docs_paper/appendix.Rmd
Reword i, c[i]

Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, partitioned into subnational units $i \in \{1, \ldots, n\}$ according to Table B.5.
We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
We modelled the probability of being in each risk group $k \in \{1, 2, 3^{+}\}$ using a multinomial logisitic regression model.
Typically, this model would be specified using a multinomial likelihood
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
\end{equation}
where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
Following the baseline category approach with $k = 1$ say, linear predictors would then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
Instead of taking this approach, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
This transformation, and further details about this model, are presented in Section 1.2.

>>>>

Let $i \in \{1, \ldots, n\}$ denote subnational units (Table B.5) which partition the 13 studied AGYW priority countries $c[i] \in \{1, \ldots, 13\}$.
We considered the years 1999-2018 denoted as $t \in \{1, \ldots, T\}$ and age groups $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$
Let the four risk groups be $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
We modelled the probability of being in each risk group $k \in \{1, 2, 3^{+}\}$ using a multinomial logisitic regression model.
Typically, this model would be specified using a multinomial likelihood
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
\end{equation}
where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
Following the baseline category approach with $k = 1$ say, linear predictors would then be specified for the additive log ratios $\log(p_{itak} / p_{ita1})$.
Instead of taking this approach, to facilitate inference in the `R-INLA`, we used an equivalent Poisson log-linear model via the multinomial-Poisson transformation [@baker1994multinomial].
This transformation, and further details about this model, are presented in Section 1.2.
